Learning Auditory Similarities Between Instrumental Playing Techniques

### 2020-05-12 paper/paper.tex
formulate questions in the ablation study

\usepackage{amsthm,amsmath}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{color}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{relsize}
% \def\includegraphic[#1]{}
% \def\includegraphics[#1]{}

@@

@@

% VL TODO: explain that this reflects a use case of browsing.
% let n be a query. (1<= n <= N').
% R: rank. number of neighbors. R=5. Typical for a user application. (display, attention span ...)
% K: number of subjects.

@@

\subsection*{Analysis}

>>>>

\usepackage{amsthm,amsmath}
\usepackage{dsfont}
\usepackage[utf8]{inputenc}
\usepackage{url}
\usepackage{color}
\usepackage{xspace}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{relsize}
\usepackage{siunitx}
% \def\includegraphic[#1]{}
% \def\includegraphics[#1]{}

@@

$\mathcal{Y}_1 (\boldsymbol{x}) = \mathcal{Y} \backslash \lbrace \boldsymbol{x} \rbrace$.

\begin{equation}
\mathbf{\Phi}_1 (\boldsymbol{x}) =
\arg \min_{\boldsymbol{y}\in \mathcal{Y}_1(\boldsymbol{x})}
\;
\big\Vert
\mathbf{L}\mathbf{\widetilde{S}}\boldsymbol{x}
-
\mathbf{L}\mathbf{\widetilde{S}}\boldsymbol{y}
\big\Vert
\end{equation}

$\mathcal{Y}_{r} (\boldsymbol{x}) = \mathcal{Y}_{(r-1)}(\boldsymbol{x}) \backslash \lbrace \mathbf{\Phi}_r (\boldsymbol{x}) \rbrace$.

\begin{equation}
\mathbf{\Phi}_r (\boldsymbol{x}) =
\arg \min_{\boldsymbol{y}\in \mathcal{Y}_r(\boldsymbol{x})}
\;
\big\Vert
\mathbf{L}\mathbf{\widetilde{S}}\boldsymbol{x}
-
\mathbf{L}\mathbf{\widetilde{S}}\boldsymbol{y}
\big\Vert
\end{equation}

@@

@@

\subsection*{Best performing system}
Our topline system comprises four computational blocks:
\begin{enumerate}
\item Joint time--frequency scattering up to a maximal time scale of $T=$\SI{1000}{\milli\second},
\item Temporal averaging at the scale of the whole musical note,
\item Median-based logarithmic compression \cite[Equation 1]{lostanlen2018extended}, and
\item Nearest neighbor search according to priorly learned non-Euclidean metric.
\end{enumerate}

\section*{Ablation study}
\subsection*{Is the dataset large enough for evaluation?}

\subsection*{Is metric learning necessary?}

\subsection*{How important is the amount of temporal context $T$?}

\subsection*{Is joint time--frequency scattering necessary?}

\subsection*{How important is feature extraction vs. metric learning?}

\section*{Analysis}
